%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Author : Radek Zobaník, Tomas Polasek (template)
% Description : First exercise in the Introduction to Game Development course.
%   It deals with an analysis of a selected title from the point of its genre, 
%   style, and mechanics.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\documentclass[a4paper,10pt,english]{article}

\usepackage[left=2.50cm,right=2.50cm,top=1.50cm,bottom=2.50cm]{geometry}
\usepackage[utf8]{inputenc}
\usepackage{hyperref}
\hypersetup{colorlinks=true, urlcolor=blue}

\newcommand{\ph}[1]{\textit{[#1]}}

\title{%
Analysis of Mechanics%
}
\author{%
[Radek] [Zobaník] ([xzoban02])%
}
\date{}

\begin{document}

\maketitle
\thispagestyle{empty}

{%
\large

\begin{itemize}

\item[] \textbf{Title:} \ph{Dishonored}

\item[] \textbf{Released:} \ph{2012}

\item[] \textbf{Author:} \ph{Arkane Studios}

\item[] \textbf{Primary Genre:} \ph{Action-adventure}

\item[] \textbf{Secondary Genre:} \ph{stealth,roleplay}

\item[] \textbf{Style:} \ph{semirealistic/stylized}

\end{itemize}

}

\section*{\centering Analysis}

You play as Corvo Attano, bodyguard of the Empress. The main gameplay is centered around the fact, that you play as that character. With the cutscenes and how people interact with you, you get the feeling that you are that person. \newline

You can decide, how you want to approach your gameplay. Missions always have many different routes that players can take. You can either focus fully on the combat aspect of the game with your sword, crossbow, spells and other goods. Or you can take more sneaky route and try not to kill anyone or to not get spotted. So you does not have to interact with the stealth part at all and the other way around.\newline

You follow a story, which develops over time. There are many notes and books lying around, that further explore the background and the world, although players does not have to collect them and read them. There are some scripted events that will only occur if you visit a certain location (like someone needs help), but in the end they will only give you some hint or more loot. There are some cutscenes and in-game dialogues with other characters that further develop the main story. In the end, players can skip optional parts of the story and focus only on the stealth/action part of the game.\newline

Even though player can make some decisions, these decisions affect the story very lightly (for example, you can choose to "spare" or kill the antagonist). The only thing that matters is your "karma". You have good "karma", if you try not to kill many people and bad "karma" is you proceed to kill many. With bad karma, locations will be more infected with rats and you will get so called "worse ending". This way, the game tries to force you into playing the game using stealth and using your weapons as a final resource. But if you want to play it like combat-oriented action game, the game will give you more of that.\newline

The genres of this game are well balanced and fully rely on the players style of gameplay. You can try to play one way or the other, but in my opinion combining the both gamestyles is the best way to experience this game. \newline

The whole game style was probably chosen to give it an industrial era vibe. It is not fully realistic, because there are magic elements, so the game has this hand drawn feeling (textures). And in my opinion this was a good decision, because with fully realistic graphic it would not have this "charm".

\end{document}
